% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (requires helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{multicol}

\setlength{\multicolsep}{0pt}

\usepackage{amssymb}
\renewcommand{\labelitemi}{\tiny$\blacksquare$}

\begin{document}

\name{Curtis W. Clemens}
\address{2706 Erlene Dr. Apt 146, Cincinnati OH, 45238 \\ (419) 343-4892}
\address{cwclemens@gmail.com \\ curtisclemens.com}
 
\begin{resume}
 
 
\section{EDUCATION} {\bf Massachusetts Institute of Technology \hfill June 2014} \\         
		{\sl Bachelor of Science,} Electrical Engineering and Computer Science \\ % \hfill GPA 3.6/5 \\
		with concentration in writing \\
		{\it Relevant Coursework:}
		\begin{multicols}{2} \begin{itemize} \setlength{\itemsep}{-2pt}
		\item Design and Analysis of Algorithms
		\item Computer Graphics
		\item Microcomputer Project Laboratory
		%\item Signals and Systems
		\item Elements of Software Construction
		%\item Artificial Intelligence
		\item Statistics for Engineers and Scientists
		\end{itemize} \end{multicols}
		
%		\vspace{2.5mm}
%		{\bf St. John's Jesuit HS \hfill June 2009}
		
 \section{EXPERIENCE} {\bf Novaro Medical Solutions \hfill July 2014 to present} \\
			{\sl Software Developer} \\
			\vspace{-4mm} \begin{itemize} \setlength{\itemsep}{-2pt}
			\item Redesigned a GUI to a SQL database used for keeping records and settings for practices, providers, insurance companies, etc.
                        \item Implemented alert system that checks database for problematic data using stored procedures and provides a summary of problems to the user with links to fix each problem.
			\item Refactored upwards of 50k lines of old code written in C\#.
			\item Debugged, maintained, and wrote documentation and user guides.
			\end{itemize}
 
\section{SKILLS} \begin{tabular}{rl}
		{\sl Programming:} & C, C++, C\#, Haskell, Java, Python \\
		{\sl Web Development:} & HTML/CSS, JavaScript \\
		{\sl Embedded Systems:} & Intel 8051, Cypress PSoC \\
                {\sl Languages:} & English, Spanish \\
		{\sl Misc.:} & Git, \LaTeX, OpenGL, SQL%, Circuit design and construction
		\end{tabular}




%\section{WORK EXPERIENCE} {\sl Personal Tutor} \hfill 2012 to present \\
%			\vspace{-4mm} \begin{itemize} \setlength{\itemsep}{-2pt}
%			\item Built and maintained a set of clients (usually between 4 and 10) by advertizing on sites like Wyzant.com and UniversityTutor.com.
%			\item Cultivated professional relationships with students that would often last many weeks.
%			\item Provided tutoring and academic support in a wide variety of subjects to students at all levels, though mostly collegiate.
%			\end{itemize}

%			


\section{EXTRA-CURRICULAR \\ ACTIVITIES}
	    
            Elected {\it Web Manager}, Theta Xi Fraternity \hfill 2012 \\
 		\vspace{-4mm} \begin{itemize} \setlength{\itemsep}{-2pt}
		\item Maintained and backed up 10TB file server.
		\item Maintained website.
		\end{itemize}

            {\sl Classical Mechanics TA}, MIT \hfill 2011 \\
    	        \vspace{-4mm} \begin{itemize} \setlength{\itemsep}{-2pt}
		\item Guided group discussions while the groups would solve problems.
		\item Answered questions and graded homework.
		\end{itemize}

	    Elected {\it House Manager}, Theta Xi Fraternity \hfill 2011 \\
		\vspace{-4mm} \begin{itemize} \setlength{\itemsep}{-2pt}
		\item Allocated \$2k budget for repairs and rennovations.
		\item Delegated work to members, logged hours, managed cleaning and construction operations.
		\item Addressed community concerns and made regular reports.
		\end{itemize}

	    Varsity Crew \hfill 2006 to 2011 \\

\end{resume}
\end{document}







